---
title: "Moderation Analysis"
author: "Ying Wang"
date: "2022-08-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Environment setup
Note: key may subject to change for everyone.
Does not have MRRC scores analysis in this file. Waiting for retrainning.
```{r}
options(java.parameters = c("-XX:+UseConcMarkSweepGC", "-Xmx8192m"))
gc()
key=keyring::key_get("qubole")
library(RJDBC)
library(tidyverse)
library(dplyr)
library(ggplot2)

driver <- JDBC("com.qubole.jdbc.jdbc41.core.QDriver", "~/Downloads/R/qds-jdbc-3.0.3.jar", identifier.quote="`")
presto <- dbConnect(driver,paste0("jdbc:qubole://presto/Presto?endpoint=https://us.qubole.com;password=",keyring::key_get("qubole")))

```


## Efficiency

### Query
The data we use is from 2022-01-01 to 2022-06-30.


#### rev --- votes detail
`rev` contains every vote from every moderator.
```{r}
rev=dbGetQuery(presto,"SELECT
    user_profile_sk
    ,content_id
    ,review_status
  FROM
    p_dwh_moderation.reported_content_logs
  WHERE
    event_type = 'REVIEW' and ds>='2022-01-01' and ds <'2022-06-30'")
```
```{r}
head(rev)
```

#### Active Moderator Geographic Data
There might be some unmatch from individual geographic info to the other geo info.
We query the neighborhood_id for each moderator and then join by `nd_city` to get city name, state, etc.
```{r Active Moderator Geographic Data}
geo=dbGetQuery(presto,"WITH moderator AS (
  SELECT
      role.user_profile_sk AS user_profile_sk
      ,MIN( last.last_dau_platform_date ) AS last_dau
      ,DATE (
        MIN( role.role_start_datetime )
      ) AS start_date
    FROM
      p_dwh_user_roles.role_status_by_day role LEFT JOIN p_dwh_general.member_last_active LAST
        ON role.user_profile_sk = last.user_profile_sk
    WHERE
      role.role IN (
        'community_reviewer'
        ,'lead'
      )
      AND role.ds >= '2022-01-01'
      AND last.last_dau_platform_date >= '2022-01-01'
    GROUP BY
      1
) 

select m.user_profile_sk,g.neighborhood_id, g.postal_code, g.city,g.county_name, g.state, g.country from
moderator m LEFT join p_dwh_general.user_geo g
on m.user_profile_sk = g.user_profile_sk")

nd_city=dbGetQuery(presto,"select neighborhood_id, city, state,country,dma_name from p_dwh_general.neighborhood_detail")

geo=geo%>%select(1,2)%>%left_join(nd_city)
```

#### Moderator Weekly Votes (`amv`)
This query gives the weekly number of vote and report from every moderator.
```{r}
#Active Moderator Votes
ecdf_df=function(vec,dt,name){
  ec=ecdf(dt)
  df=data.frame(vec,prop=ec(vec))
  colnames(df)[1]=name
  return(df)
}

amv= dbGetQuery(presto,"select user_profile_sk, date_diff (
      'day'
      ,date('2022-01-01')
      ,date(ds)
    ) / 7 AS time_n_22,
	event_type,
	 count(event_type)
	 
from p_dwh_moderation.reported_content_logs
where ds>='2022-01-01' and ds< '2022-06-30'
group by 1, 3,2
order by 1, 3,2")

```

#### Active Moderator Weekly Session Count (`ams`)

It seems the table `p_dwh_activity.session_agg_utc` is not available any more
```{r} 
# 
# ams= dbGetQuery(presto,"WITH moderator AS (
#   SELECT
#       role.user_profile_sk AS user_profile_sk
#       ,MIN( last.last_dau_platform_date ) AS last_dau
#       ,DATE (
#         MIN( role.role_start_datetime )
#       ) AS start_date
#     FROM
#       p_dwh_user_roles.role_status_by_day role LEFT JOIN p_dwh_general.member_last_active LAST
#         ON role.user_profile_sk = last.user_profile_sk
#     WHERE
#       role.role IN (
#         'community_reviewer'
#         ,'lead'
#       )
#       AND role.ds >= '2022-01-01'
#       AND last.last_dau_platform_date >= '2022-01-01'
#     GROUP BY
#       1
# ) SELECT
#     m.user_profile_sk
#     ,m.last_dau
#     ,m.start_date
#     ,date_diff (
#       'day'
#       ,DATE ('2022-01-01')
#       ,DATE (s.ds)
#     ) / 7 AS time_n_22
#     ,count (s.session_event_id) AS weekly_sessions_count
#   FROM
#     moderator m LEFT JOIN p_dwh_activity.session_agg_utc s
#       ON m.user_profile_sk = s.user_profile_sk
# 	WHERE s.ds>='2022-01-01'
#   GROUP BY
#     1
#     ,2
#     ,3
#     ,4
# 
#   ORDER BY
#     1
#     ,4
# ")
# 

```

#### Results and reasons
```{r}
reason_t= dbGetQuery(presto,"select * from p_dwh_constants.content_report_reason_constants")
reasons= dbGetQuery(presto,"SELECT
    content_id
    ,source_neighborhood_id as neighborhood_id
    ,content_type
    ,report_cnt
    ,report_reasons
	,review_cnt
	,review_remove_cnt as remove_cnt
	,review_consider_removing_cnt as c_remove_cnt
	,review_dont_remove_cnt as dont_cnt
	,moderation_removed_ind as removal
	,moderation_keep_ind as keep
	,date_diff('minute',first_report_datetime,last_review_datetime) as process_time
  FROM
    p_dwh_moderation.reported_content_detail 
	where date_format(content_creation_datetime,'%Y-%m-%d') >= '2022-01-01' 
	and date_format(content_creation_datetime,'%Y-%m-%d') < '2022-06-30'")
```

### Analysis
#### Preprocess
`amvt` holds just the weekly number of votes from every moderator. `time_n_22` is the number of weeks from 01-01.
```{r}
colnames(amv)[4]='count'
amv=amv%>%mutate(time_n_22=as.integer(time_n_22),
                 count=as.integer(count))

# ams=ams%>%mutate(time_n_22=as.integer(time_n_22),
#                  weekly_sessions_count=as.integer(weekly_sessions_count))

amvt=amv%>%filter(event_type=="REVIEW")%>%group_by(user_profile_sk,time_n_22)%>%summarise(count=sum(count))
```

Restrict the scale to be just US
```{r}
geo=geo%>%filter(country=="US")
amvt=geo%>%select(user_profile_sk)%>%inner_join(amvt)
# ams=geo%>%select(user_profile_sk)%>%inner_join(ams)
```


#### How many Moderators do we have?
```{r}
n_distinct(geo$user_profile_sk)
```
418679 moderators logged in to the platform at least once this Year.

```{r}
n_distinct(amvt$user_profile_sk)
156757/413803
```
156757 voted at least once. 37.9% of the ones who logged in.


```{r}
votes_total=amvt%>%group_by(user_profile_sk)%>%summarise(votes=sum(count))
```


#### Votes number distribution
prop = proportion of moderators voted less or equal to N votes.
This table shows the percentage of moderators who voted n times or less.
```{r}
ecdf_df(c(1,5,10,15,30,45,60,75,100,150,200,250,350,500),votes_total$votes,"votes")%>%mutate(prop=prop%>%round(3)*100)
```

Rank moderators by the number of votes they voted.
`cum_per` is (the cumulative sum of the votes by the first N moderators / all votes)
```{r}
votes_ranked=votes_total%>%arrange(desc(votes))%>%mutate(cum_per=cumsum(votes)/sum(votes))
votes_ranked%>%mutate(rank=1:length(votes))%>%mutate(first10=(rank<=16000))%>%group_by(first10)%>%summarise(votes=sum(votes))
votes_ranked
```

Check the cumulative proportion of votes by first 16000, 32000, 48000 moderators. (First 10% 20% 30%)
```{r}
#Check the cum
votes_ranked%>%mutate(rank=1:length(votes),cum_per=cum_per%>%round(3)*100)%>%
  slice(16000,32000,48000,53000,72000)%>%
  rename()
```


#### results count and votes required
```{r distribution of results}
reasons=reasons%>%filter(!is.na(report_reasons))%>%
  left_join(nd_city)%>%
  filter(!(removal==1&keep==1),country=="US")%>%
  mutate(points=3*remove_cnt+c_remove_cnt-3*dont_cnt)%>%
  mutate(result=case_when(removal==1 | points>=9~"REMOVAL",
                                  keep==1 | points <=(-9)~"KEEP",
                                  review_cnt<=4~"NO_DECISION_4_OR_LESS",
                                  TRUE~"NO_DECISION_5_OR_MORE"))%>%
  mutate(process_time=as.integer(process_time)/60)

reasons%>%count(result)%>%mutate(prop=(n/sum(n)*100)%>%round(1))%>%arrange(c(4,1,2,3))
```



```{r}
reasons%>%count(result)%>%filter(result!="NO_DECISION_4_OR_LESS")%>%mutate(prop=(n/sum(n)*100)%>%round(1))
```
`reasons2` filter out abnormal posts
```{r votes taken by result}
reasons2=reasons%>%
  filter(points<=12 & points>=(-12))

keep_votes=reasons2%>%
  count(result,review_cnt)%>%
  group_by(result)%>%
  mutate(prop=(n/sum(n)*100)%>%round(1))%>%
  mutate(cum_prop=cumsum(prop))%>%
  filter(review_cnt%in%c(0:15,20),result=="KEEP")%>%
  rename(votes=review_cnt)

removal_votes=reasons2%>%
  count(result,review_cnt)%>%
  group_by(result)%>%
  mutate(prop=(n/sum(n)*100)%>%round(1))%>%
  mutate(cum_prop=cumsum(prop))%>%
  filter(review_cnt%in%c(0:15,20),result=="REMOVAL")%>%
  rename(votes=review_cnt)

no_decision_votes=reasons2%>%
  count(result,review_cnt)%>%
  filter(result%in%c("NO_DECISION_4_OR_LESS","NO_DECISION_5_OR_MORE"))%>%
  mutate(prop=(n/sum(n)*100)%>%round(1))%>%
  mutate(cum_prop=cumsum(prop))%>%
  filter(review_cnt%in%c(0:15,20))%>%
  rename(votes=review_cnt)

keep_votes
removal_votes
no_decision_votes
```


There are some abnormal rows: points go beyond 9/-9. I wonder if the resolved posts be removed from the queues of moderators who haven't voted on it.

example: content_id=225887517
  3 more votes after the decision made for REMOVAL
  
Don't know how often this is. 78,117 posts points>=12. 6% of all removed, not too bad.

```{r abnormal posts}
reasons%>%filter(points<=(-12))
reasons%>%filter(points>=(12))
```

#### Removal Time
```{r Removal Time Table}
reasons%>%
  filter(result=="REMOVAL",process_time<24*30)%>%
  summarise(average_time=mean(process_time,na.rm=T),
  median_time=median(process_time,na.rm=T),
  perc_75=quantile(process_time,.75,na.rm=T),
  perc_90=quantile(process_time,.90,na.rm=T))
```


```{r}
ecdf_df(c(1,6,12,18,24,36,48,12*7,12*15),votes_removal$process_time,"removal_time")
```


### dma Efficiency
```{r dma Removal Time Table}
dma_time=reasons%>%
  filter(result=="REMOVAL",process_time<24*30)%>%
  group_by(dma_name)%>%
  summarise(average_time=mean(process_time,na.rm=T),
  median_time=median(process_time,na.rm=T),
  perc_75=quantile(process_time,.75,na.rm=T),
  perc_90=quantile(process_time,.90,na.rm=T))

dma_result=reasons%>%
  group_by(dma_name)%>%
  count(result)%>%
  pivot_wider(names_from=result,values_from = n)

dma_efficiency=reasons%>%
  count(dma_name)%>%
  arrange(desc(n))%>%
  rename(reported=n)%>%
  left_join(dma_result)%>%
  left_join(dma_time)%>%
  mutate(under_voted_prop=NO_DECISION_4_OR_LESS/reported,
         potential_efficiency_gain=NO_DECISION_4_OR_LESS*0.7)%>%
  mutate(report_bins=cut(reported,c(0,200,500,1000,5000,10000,Inf)),
         under_v_bins=cut(under_voted_prop,c(0,0.1,0.2,0.3,0.4,0.6,Inf)))

dma_efficiency%>%count(under_v_bins)
dma_efficiency%>%arrange(desc(potential_efficiency_gain))%>%select(dma_name,reported,potential_efficiency_gain)
```
#### median_removal_time vs. under_voted_prop
```{r}
dma_efficiency%>%filter(reported>300)%>%
  ggplot(aes(x=under_voted_prop,y=median_time))+
  geom_point()+
  geom_smooth(method="lm")
```

#### Under-voting vs. number of reports
```{r}
dma_efficiency%>%
  {boxplot(under_voted_prop~report_bins,data=.,names=c("0-200","200-500","500-1k","1k-5k","5k-10k","10k+"))}
```


## Overall Accuracy by reason

Take the top 3 reported reason for each post.
```{r}
reasons_sep=reasons%>%select(content_id,report_reasons)%>%separate_rows(report_reasons,sep=",")%>%mutate(report_reasons=as.integer(report_reasons))

reasons_cnt=reasons_sep%>%count(content_id,report_reasons)
reasons_first_3=reasons_cnt%>%group_by(content_id)%>%arrange(desc(n))%>%slice(1:3)
reasons_first_3=reasons_first_3%>%mutate(reason_num=c("reason1","reason2","reason3")[1:length(n)])%>%rename(reason_value=report_reasons)%>%left_join(reason_t%>%select(-3))

reasons_first_3%>%ungroup%>%count(reason_num)
1.5/24.15
```
About 6% reported for 2+ reasons.

Category
```{r}
catg_top_3=reasons_cnt%>%rename(reason_value=report_reasons)%>%left_join(reason_t%>%select(reason_value,reason_category))%>%group_by(content_id,reason_category)%>%summarise(n=sum(n))%>%arrange(desc(n))%>%slice(1:3)
catg_top_3=catg_top_3%>%mutate(reason_num=c("cat1","cat2","cat3")[1:length(n)])
catg_top_3%>%ungroup()%>%count(reason_num)
```
About 4.5% reported for 2+ categories.

```{r}
catg_wide=catg_top_3%>%select(-n)%>%pivot_wider(names_from=reason_num,values_from = reason_category)
reasons=reasons%>%left_join(catg_wide)%>%rename(reason1=cat1,reason2=cat2,reason3=cat3)%>%filter(!is.na(reason1))

reasons_long=reasons%>%pivot_longer(reason1:reason3,names_to = "reason_num",values_to="reason")%>%filter(!is.na(reason))
reasons_long


```
Removal Rate by Reason
```{r}
reasons_freq=reasons_long%>%count(reason)%>%mutate(prop=100*(n/sum(n))%>%round(3))
top5_reason=reasons_freq%>%arrange(desc(n))%>%slice(1:7)%>%select(reason)

result_by_reason=reasons_long%>%count(reason,result)%>%group_by(reason)%>%mutate(prop=100*(n/sum(n))%>%round(3))

result_by_reason_sufficient=result_by_reason%>%filter(result%in%c("REMOVAL","KEEP"))%>%mutate(prop=100*(n/sum(n))%>%round(3))
result_by_reason_sufficient%>%filter(result=="REMOVAL")%>%arrange(desc(n))

result_by_reason

result_by_reason_sufficient
```


removal votes by reason
```{r}
votes_by_reason=reasons_long%>%
  filter(result=="REMOVAL")%>%
  group_by(reason)%>%
  summarise(mean_votes=mean(review_cnt),
            median_votes=median(review_cnt),
            votes_75=quantile(review_cnt,0.75),
            votes_90=quantile(review_cnt,0.9))
votes_by_reason
```

### dma Accuracy
```{r}
removal_rate_by_reason_by_dma=reasons_long%>%count(dma_name,reason,result)%>%
  filter(result%in%c("REMOVAL","KEEP"),reason%in%unlist(top5_reason))%>%
  group_by(dma_name,reason)%>%
  mutate(prop=100*(n/sum(n))%>%round(3))%>%
  left_join(dma_efficiency%>%
              select(dma_name,reported,under_voted_prop,under_v_bins))%>%
  arrange(desc(reported))%>%
  filter(result=="REMOVAL")

dma_accuracy_gain=removal_rate_by_reason_by_dma%>%
  left_join(result_by_reason_sufficient%>%
              select(reason,result,ref_prop=prop))%>%
  mutate(deviation=prop-ref_prop)%>%
  mutate(potential_efficiency_gain=(deviation/100*(n/(prop/100)))%>%round(1))
dma_accuracy_gain
```

```{r}
dma_accuracy_gain%>%filter(reason=="Offensive",reported>500)%>%
  {hist(.$deviation,breaks=20,main="Histogram of dma offensive deviation")}
```

```{r}
dma_accuracy_gain%>%filter(reason=="Offensive",reported>500)%>%
  ggplot(aes(x=under_voted_prop,y=abs(deviation)))+
  geom_point()+
  geom_smooth(method="lm")
  
```

```{r}
dma_accuracy_gain%>%filter(reason=="Offensive",reported>500)%>%
  {boxplot(abs(deviation)~under_v_bins,data=.)}

```


```{r}
dma_accuracy_gain_agg=dma_accuracy_gain%>%group_by(dma_name)%>%summarise(potential_efficiency_gain=sum(abs(potential_efficiency_gain)))%>%arrange(desc(potential_efficiency_gain))
dma_accuracy_gain_agg
```




## By city
### City Efficiency 
```{r city Removal Time Table}
city_time=reasons%>%
  filter(result=="REMOVAL",process_time<24*30)%>%
  group_by(state,city)%>%
  summarise(average_time=mean(process_time,na.rm=T),
  median_time=median(process_time,na.rm=T),
  perc_75=quantile(process_time,.75,na.rm=T),
  perc_90=quantile(process_time,.90,na.rm=T))

city_result=reasons%>%
  group_by(state,city)%>%
  count(result)%>%
  pivot_wider(names_from=result,values_from = n)

city_efficiency=reasons%>%
  count(state,city)%>%
  arrange(desc(n))%>%
  rename(reported=n)%>%
  left_join(city_result)%>%
  left_join(city_time)%>%
  mutate(under_voted_prop=NO_DECISION_4_OR_LESS/reported,
         potential_efficiency_gain=NO_DECISION_4_OR_LESS*0.7)%>%
  mutate(report_bins=cut(reported,c(0,200,500,1000,5000,10000,Inf)),
         under_v_bins=cut(under_voted_prop,c(0,0.1,0.2,0.3,0.4,0.6,Inf)))

city_efficiency%>%count(under_v_bins)
city_efficiency%>%arrange(desc(potential_efficiency_gain))%>%select(state,city,reported,potential_efficiency_gain)
```


```{r}
city_efficiency%>%filter(reported>500)%>%
  ggplot(aes(x=under_voted_prop,y=median_time))+
  geom_point()+
  geom_smooth(method="lm")
```
```{r}

city_efficiency%>%filter(reported>500)%>%
  ggplot(aes(x=under_voted_prop,y=perc_75))+
  geom_point()+
  geom_smooth(method="lm")
```




```{r}
city_efficiency%>%
  {boxplot(under_voted_prop~report_bins,data=.,names=c("0-200","200-500","500-1k","1k-5k","5k-10k","10k+"))}
```


```{r}

city_accuracy=city_efficiency%>%filter(REMOVAL>100)%>%mutate(removal_rate=REMOVAL/(REMOVAL+KEEP))

city_accuracy%>%{hist(.$removal_rate,breaks=20)}
```


### City Accuracy
```{r}
removal_rate_by_reason_by_city=reasons_long%>%count(state,city,reason,result)%>%
  filter(result%in%c("REMOVAL","KEEP"),reason%in%unlist(top5_reason))%>%
  group_by(state,city,reason)%>%
  mutate(prop=100*(n/sum(n))%>%round(3))%>%
  left_join(city_efficiency%>%
              select(state,city,reported,under_voted_prop,under_v_bins))%>%
  arrange(desc(reported))%>%
  filter(result=="REMOVAL")

city_accuracy_gain=removal_rate_by_reason_by_city%>%
  left_join(result_by_reason_sufficient%>%
              select(reason,result,ref_prop=prop))%>%
  mutate(deviation=prop-ref_prop)%>%
  mutate(potential_efficiency_gain=(deviation/100*(n/(prop/100)))%>%round(1))
```

```{r}
city_accuracy_gain%>%filter(reason=="Offensive",reported>500)%>%
  {hist(.$deviation,breaks=20,main="Histogram of city offensive deviation")}
```

```{r}
city_accuracy_gain%>%filter(reason=="Offensive",reported>500)%>%
  ggplot(aes(x=under_voted_prop,y=abs(deviation)))+
  geom_point()+
  geom_smooth(method="lm")
```

```{r}
city_accuracy_gain%>%filter(reason=="Offensive",reported>200)%>%
  {boxplot(abs(deviation)~under_v_bins,data=.)}
```


```{r}
city_accuracy_gain_agg=city_accuracy_gain%>%
  group_by(state,city)%>%
  summarise(potential_efficiency_gain=sum(abs(potential_efficiency_gain)))%>%
  arrange(desc(potential_efficiency_gain))
city_accuracy_gain_agg

city_accuracy_gain%>%
  select(-c(result,reported,state,under_voted_prop,under_v_bins))%>%
  rename(removal=n,removal_rate=prop,ref_removal_rate=ref_prop)
```
